---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# convertR

<!-- badges: start -->
<!-- badges: end -->

The goal of convertR is to convert one unit into another.

## Installation

You can install the development version of convertR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LucaKeiser/convertR")
```

## Load the package
```{r example}
library(convertR)
```


## Examples

This is a basic example which shows you how to solve a common problem:

### Temperature

#### 1) from degree Celsius to degree Fahrenheit:
```{r}
celsius_to_fahrenheit(100)
```

#### 2) from degree Celsiusi to degree Kelvin:
```{r}
celsius_to_kelvin(100)
```

#### 3) form degree Fahrenheit to degree Celsius:
```{r}
fahrenheit_to_celsius(100)
```

#### 4) from degree Fahrenheit to degree Kelvin:
```{r}
fahrenheit_to_kelvin(100)
```

### You could also do a table

```{r}
# load additional packge
library(tidyverse)

input_celsius <- 100
tibble(
  input_celsius = input_celsius,
  fahrenheit = celsius_to_fahrenheit(input_celsius),
  kelvin = celsius_to_kelvin(input_celsius)
) %>% 
  knitr::kable()
```


