---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# convertR

<!-- badges: start -->
<!-- badges: end -->

The goal of convertR is to convert one unit into another.

## Installation

You can install the development version of convertR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LucaKeiser/convertR")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(convertR)
## basic example code
```


### 1) from degree Celsius to degree Fahrenheit
```{r}
celsius_to_fahrenheit(100)
```

### 2) from degree Celsiusi to degree Kelvin
```{r}
celsius_to_kelvin(100)
```

### 3) form degree Fahrenheit to degree Celsius
```{r}
fahrenheit_to_celsius(100)
```

### 4) from degree Fahrenheit to degree Kelvin
```{r}
fahrenheit_to_kelvin(100)
```

